\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
correcting citations for the two-loop tadpoles in the MSSM and NMSSM

If higher accuracy is required additional routines with higher order
corrections can be added by setting \code{UseHiggs2LoopMSSM = True}
in the model file.  For example in the MSSM by default \fs adds two
two-loop Higgs FORTRAN routines supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
to add two loop corrections of $\oatas$, $\oabas$, $\oatq$,
$\oabq$, $\oatauq$ and $\oatab$.  In the NMSSM
contributions of the order $\oatas$, $\oabas$ \cite{Degrassi:2009yq}
can be added by setting \code{UseHiggs2LoopNMSSM = True} in the model
file.

>>>>

If higher accuracy is required additional routines with higher order
corrections can be added by setting \code{UseHiggs2LoopMSSM = True}
in the model file.  For example in the MSSM by default \fs adds
two-loop Higgs FORTRAN routines supplied by P.~Slavich from
\cite{Dedes:2002dy,Dedes:2003km}
to add two-loop corrections of $\oatas$, $\oabas$, $\oatq$,
$\oabq$, $\oatauq$ and $\oatab$.  In the NMSSM the same contributions
can be added by setting \code{UseHiggs2LoopNMSSM = True} in the model
file.
